Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2013-11-21 paper.tex
Submitted version. Reverted Inkscape graphics to origionals.

\author{Mark~H.~Jones,~Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}

@@

\thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: jonathanscott@iee.org.}

@@

\begin{figure}
    \begin{center}
    \includegraphics{graphics/StJudeOctrodeDiagram3}
    \end{center}
    \caption{St. Jude Medical Octrode lead comprised of eight coaxial cylindrical platinum electrodes (1mm in diameter, 3mm long) separated by 4mm insulating spacers.}
    \label{fig:octrode}
\end{figure}

@@

\begin{figure}
    \begin{center}
        \includegraphics{graphics/sheepSpine2}
    \end{center}
    \caption{Cross section of a sheep spine showing the position of the electrode array relative to the dura. Spotted regions represent cross sectioned vertebrae.}
    \label{fig:sheepSpine}
\end{figure}

>>>>

\author{Mark~H.~Jones and Jonathan~Scott,~\IEEEmembership{Senior Member,~IEEE}

@@

\thanks{Jonathan Scott is with the School of Electronic Engineering, University of Waikato, New Zealand, e-mail: jonathanscott@ieee.org.}

@@

\begin{figure}
    \begin{center}
    \includegraphics{graphics/StJudeOctrodeDiagram}
    \end{center}
    \caption{St. Jude Medical Octrode lead comprised of eight coaxial cylindrical platinum electrodes (1mm in diameter, 3mm long) separated by 4mm insulating spacers.}
    \label{fig:octrode}
\end{figure}

@@

\begin{figure}
    \begin{center}
        \includegraphics{graphics/sheepSpine}
    \end{center}
    \caption{Cross section of a sheep spine showing the position of the electrode array relative to the dura. Spotted regions represent cross sectioned vertebrae.}
    \label{fig:sheepSpine}
\end{figure}
